---
title: "Analysis of the Global Extreme Poverty "
author: "Group16"
date: "2022/2/16"
output:
  pdf_document:
    latex_engine: pdflatex
    number_sections: yes
    keep_tex: true
  html_document:
    df_print: paged
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyverse)
library(ggplot2)
library(skimr)
library(GGally)
library(olsrr)

```

# Introduction 
Most people in the world are in the poverty. This analysis is aim to explore the global extreme poverty, which is considered a person if they live on less than 1.90 dollars per day, defined by the United Nation. 
We have used 5 data sets to analyze extreme poverty. The distribution of population between different poverty thresholds from 1981 to 2017, total GDP, and the total expenditure as a share of GDP for that year in health care, education, and military. In this report, we just focus on 2012 to 2017. We will be discussing two questions:
1. What is the state of extreme poverty in the world? And the prediction of the population of extreme poverty.
2. How do these factors influence extreme poverty in the world? 


# Exploratory Data Analysis  
## What is the state of extreme poverty in the world?
As defined by the World Bank, extreme poverty 
```{r inputdata}
GDP_raw <- read.csv("gdp-per-capita-worldbank.csv")
edu_raw <- read.csv("total-government-expenditure-on-education-gdp.csv")
health_raw <- read.csv("total-healthcare-expenditure-gdp.csv")
poverty_raw <- read.csv("total-population-in-extreme-poverty.csv")
military_raw <- read.csv("military-expenditure-share-gdp-sipri.csv")
```

